\xavier{Measuring precise radia velocities and cross-correlation function line-profile variations using a Skew Normal distribution}

### 2018-05-15 manuscript.tex
Intro updated

%\abstract
{\bf Abstract}\\
% Context, Aims, Methods, Results, Conclu (not mandatory)
\xavier{Stellar activity is the main limitation to the detection of small-mass exoplanets using the radial-velocity (RV) technique. Stellar activity can be probed by measuring the cross-correlation function (CCF) shape variations as a function of time. Those variations are measured using the different moments of the CCF, therefore measuring with the best precision all the different moments of the CCF is crucial} to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.

We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry. Since the CCF presents a natural asymmetry due to convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.

@@

We strongly encourage the use of the SN distribution to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
\comment{You simply cannot make this claim. What you have shown is that the SN method produces errors that are 60\% larger than the Normal distribution and you hint that this is due to it being more sensitive to activity. You have not demonstrated this by looking at the "activity" signal that the SN isolates to see if it is actually more sensitive at finding rotation periods, activity cycles, etc. Where is the sensitivity in actually getting out useful information? Furthermore, after correcting the SN RVs for the activity, you arrive at the same answer as the Normal distribution method. I would conclude that the SN offers no real advantages over Normal so the community can continue to use the standard method.
Grammatically this is an ambiguous statement. Are you looking for "better signals", i.e. ones that you like, or probing stellar signals in a better way? (This is what you meant, but not what was stated.)}
%\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}

@@

\xavier{When working with radial velocities, the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induce by the stars we are observing \citep[][]{Dumusque:2017aa}. Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs. It is therefore mandatory to understand better stellar signals and to find ways to correct for them if in the near future, we want to detect or confirm an Earth-twin planet. This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{Fischer:2017aa} should have the stability to detect such signals. However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar activity effect on CCF, Normal fit plus FWHM indicator}
\jessi{Eventually three methods are introduced for detecting CCF asymmetry:  FWHM, bisector span, and the Figueira approach - it seems that these methods need to be better explained.  Somewhere in the intro it needs to become clear that we are (i) providing a new way of measuring CCF asymmetry, (ii) this is a unified approach that also provides an RV estimate, and (iii) it (hopefully) provides a better indicator.}

Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity. Stellar activity creates magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}. To differentiate between the signal induced by a planet and the one induced by stellar activity, a common technique used is tu study the different moments of the cross-correlation function (CCF). The CCF, obtained by

@@

For stabilized spectrographs, the RV is derived by first correlating a stellar spectrum at a particular time with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).  The CCF is a function of RV, and the RV corresponding to the minimum of the CCF is the estimated RV for that spectrum.  However, this would give a noisy estimate so first a Normal density shape is fitted to the CCF, and then the estimated mean of the Normal density is used as the estimate of the RV.  The full width at half maximum (FWHM) of the Normal fit is also used as an indicator of spectral line asymmetry.
The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.

The convection in external layers of solar type stars is responsible for the granulation pattern than can be seen at high spatial resolution on the surface of the Sun. The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}. 
\comment{Regarding the C-shape of the bisector. The classic C-shape is only for late-type stars. In fact for hotter stars (F-type) it reverses.
The strength of the asymmetry depends not just on the velocities, it is more complicated than that. It also depends on the flux ratio between hot cells and cool lanes, as well as the ratio of surface areas between the two.}
The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}. Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution can be an appropriate model for the CCF. This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
\comment{But the activity causes the asymmetry to change due to rotation, spot evolution, etc. The authors are confusing the readers here. They talk about a changing activity signal, but now argue that the precision is only kept if the asymmetry is constant, which it is not. I think what they want to say is that you measure a precise stellar radial velocity, but the activity makes its own contribution which reduces the accuracy of the RV determination for the barycentric motion due to a planet.}

Convection is not the only phenomenon responsible for asymmetries in the single spectral line and the CCF. Stellar activity is responsible for the appearance of dark spots and bright faculae on the stellar photosphere, which breaks the flux balance between the red-shifted and the blue-shifted halves of a rotating star and therefore induce an asymmetry of spectral lines and thus of the CCF. As the star rotates, spots and faculae move across the stellar disk, modifying the line asymmetry and thus producing an apparent Doppler shift \citep{Saar-1997b,Hatzes-2002,Kurster2003,Desort-2007,Lagrange-2010,Boisse-2012b}. Spots and faculae are also regions where the magnetic field is strong. Strong magnetic fields reduce stellar convection, which in turn modifies the asymmetry of spectral lines \citep[][]{Cavallini-1985a,Dravins-1981,Lindegren-2003,Meunier-2010a,Dumusque-2014b}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bisector span indicators of stellar activity}
\jessi{Its seems that more details should be added here}
Stellar activity can induce RV variations by a modification of the spectral line asymmetry, while any orbiting companions would induce a pure Doppler shift on \emph{all} spectral lines without modifying their shape.
Therefore, assuming that there is no instrumental systematics, stellar activity generally induces a variation in line asymmetry that can be observed in the  FWHM of the CCF. 
The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}. 
An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines. To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}. A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity. 
\comment{It is the slope or span, not both. And you generally do not calculate the inverse, just the
span. This may be correlated or inversely correlated with the RV.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Figueira indicators of stellar activity}
\citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF \jessi{this needs to be better explained}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Issues with detecting stellar activity}
Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry. All those parameters are correlated when stellar activity is dominant, and performing a step-by-step approach makes it difficult to correctly derive the errors on the different parameters retrieved. 
\comment{I simply do not understand this statement, possibly because it does not follow a standard English construction. You have a CCF and you measure a width and bisector span. This is a measurement error determined by the S/N, the resolution, and the stability of the spectrograph. You can determine an error in a quantity (RV and BIS). You can also have an uncertainty in the contribution of activity to the RV signal, but that is not a formal error. True errors come from photon statistics, systematic errors, instrumental errors, etc. You can attempt to remove the signal due to activity and that has an associated error, but that error is due to your lack of knowledge of the surface structure causing this RV and the exact value of the contribution to the RV. This is different from a measurement error. Maybe that is what you mean here, but it is not clear from what is written.}
In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors. We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Outline of paper}
\todo{This paragraph will need to be updated once the rest is finished.} The paper is organized as follow. In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN density is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF. In Sec.~\ref{intro} we present a simple model to correct for stellar activity. In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators. In Sec.~\ref{sec:5} we derive error bars for the different CCF parameters, and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.

>>>>

%\abstract
{\bf Abstract}\\
% Context, Aims, Methods, Results, Conclu (not mandatory)
\xavier{Stellar activity is the main limitation to the detection of small-mass exoplanets using the radial-velocity (RV) technique. Stellar activity can be probed by measuring the cross-correlation function (CCF) shape variations as a function of time. Those variations are measured using the different moments of the CCF, therefore measuring with the best precision those moments is crucial} to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.

We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry induced by convective blueshift.
%. Since the CCF presents a natural asymmetry due to convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.

@@

\xavier{We strongly encourage the use of the SN distribution rather than the Normal distribution, because this allows to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals and because the standard errors on the RV and the the asymmetry are smaller.}
% than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
\xavier{I just left this comment here so that we can check at the end that we answered to all referee's major comments, however, I believe it is not relevant anymore with our new analysis.}\comment{You simply cannot make this claim. What you have shown is that the SN method produces errors that are 60\% larger than the Normal distribution and you hint that this is due to it being more sensitive to activity. You have not demonstrated this by looking at the "activity" signal that the SN isolates to see if it is actually more sensitive at finding rotation periods, activity cycles, etc. Where is the sensitivity in actually getting out useful information? Furthermore, after correcting the SN RVs for the activity, you arrive at the same answer as the Normal distribution method. I would conclude that the SN offers no real advantages over Normal so the community can continue to use the standard method.
Grammatically this is an ambiguous statement. Are you looking for "better signals", i.e. ones that you like, or probing stellar signals in a better way? (This is what you meant, but not what was stated.)}
%\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}

@@

\xavier{When working with radial velocities, the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induce by the stars we are observing \citep[][]{Dumusque:2017aa}. Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs. It is therefore mandatory to understand better stellar signals and to find ways to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique. This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{Fischer:2017aa} should have the stability to detect such signals. However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar activity effect on CCF, Normal fit plus FWHM and BIS SPAN indicators}
\jessi{Eventually three methods are introduced for detecting CCF asymmetry:  FWHM, bisector span, and the Figueira approach - it seems that these methods need to be better explained.  Somewhere in the intro it needs to become clear that we are (i) providing a new way of measuring CCF asymmetry, (ii) this is a unified approach that also provides an RV estimate, and (iii) it (hopefully) provides a better indicator.}

\xavier{Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity. Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}. In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, that will shift the entire stellar spectrum, and stellar activity that modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}. However, on quiet GKM dwarfs, the main target for precise RV measurements, stellar activity induce signals of a few \ms. This corresponds physically to variations smaller than 1/100th of a pixel on the detector.
% and at this level it is extremely difficult to differentiate between a pure shift and a change in line shape. 
To be able to measure such tiny variations, we average the information of all the line in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}. 
%Although this process allows to measure spectral shifts at the level smaller than the meter-per-second, by averaging all the lines together we also average out line shape variation which make it more difficult to differentiate between a pure Dopler-shift and line shape variation.
The result of this operation gives us the cross-correlation function (CCF). To measure the Doppler-shift between different spectra, and therefore get the RV of a star as a function of time, we calculate the variations of the CCF barycenter. The barycenter is generally estimated by fitting a Normal distribution to the CCF, and taking its mean. Variation in line shape between different spectra, which indicate the presence of signals induced by stellar activity, is measured by analysing the different moments of the CCF. Generally, the width of the CCF is estimated using the FWHM of the fitted Normal distribution, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
%bisector \citep[][]{Voigt1956}, the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
}

\subsection{Why FWHM and BIS SPAN important?}

\xavier{If a RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep[e.g.][]{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}. It is therefore common now, that when fitting for a planetray signal, in addition to a Keplerian, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}. It is also common to add a Gaussian process to the model to account for the correlated noise induced by stellar activity. The hyperparameters of the Gaussian process are generally trained on the different activity indicators \citep[e.g.][]{Haywood-2014,Rajpaul-2015}. It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated to the RVs but also for which we can obtain the best precision.}

\subsection{Figueira indicators of stellar activity + other}
\xavier{Several works have derived indicators that are more sensitive to line asymmetry than the BIS SPAN. In \citet{Boisse-2011}, the authors develop $V_{span}$ a new indicator to derive the CCF asymmetry, that is more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR). \citet{Figueira-2013} studied the use of two new indicators, bi-Gauss and $V_{asy}$. The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger, therefore allowing the detection of smaller-amplitude correlations with radial-velocity variations. They also demonstrated that $V_{asy}$ seems to be the best indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any other asymmetry indictors.
}

\subsection{Why using a SN distribution?}
\xavier{In all the method described above, the RV and the FWHM is derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach. In this paper we propose to use a Skew Normal (SN) distribution to derive at the same time the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}. In addition, we know that for solar-type stars and cooler dwarfs, the bisector of the CCF as a "C"-shape due to convective blueshift \citep[e.g.][]{Dravins-1981, Gray-2009}. Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN distribution, should give more precise results.
}

@@

%For stabilized spectrographs, the RV is derived by first correlating a stellar spectrum at a particular time with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).  The CCF is a function of RV, and the RV corresponding to the minimum of the CCF is the estimated RV for that spectrum.  However, this would give a noisy estimate so first a Normal distribution shape is fitted to the CCF, and then the estimated mean of the Normal distribution is used as the estimate of the RV.  The full width at half maximum (FWHM) of the Normal fit is also used as an indicator of spectral line asymmetry.
%The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.

%The convection in external layers of solar type stars is responsible for the granulation pattern than can be seen at high spatial resolution on the surface of the Sun. The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}. 
%\comment{Regarding the C-shape of the bisector. The classic C-shape is only for late-type stars. In fact for hotter stars (F-type) it reverses.
%The strength of the asymmetry depends not just on the velocities, it is more complicated than that. It also depends on the flux ratio between hot cells and cool lanes, as well as the ratio of surface areas between the two.}
%The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}. Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution can be an appropriate model for the CCF. This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
%\comment{But the activity causes the asymmetry to change due to rotation, spot evolution, etc. The authors are confusing the readers here. They talk about a changing activity signal, but now argue that the precision is only kept if the asymmetry is constant, which it is not. I think what they want to say is that you measure a precise stellar radial velocity, but the activity makes its own contribution which reduces the accuracy of the RV determination for the barycentric motion due to a planet.}
%
%
%Convection is not the only phenomenon responsible for asymmetries in the single spectral line and the CCF. Stellar activity is responsible for the appearance of dark spots and bright faculae on the stellar photosphere, which breaks the flux balance between the red-shifted and the blue-shifted halves of a rotating star and therefore induce an asymmetry of spectral lines and thus of the CCF. As the star rotates, spots and faculae move across the stellar disk, modifying the line asymmetry and thus producing an apparent Doppler shift \citep{Saar-1997b,Hatzes-2002,Kurster2003,Desort-2007,Lagrange-2010,Boisse-2012b}. Spots and faculae are also regions where the magnetic field is strong. Strong magnetic fields reduce stellar convection, which in turn modifies the asymmetry of spectral lines \citep[][]{Cavallini-1985a,Dravins-1981,Lindegren-2003,Meunier-2010a,Dumusque-2014b}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Bisector span indicators of stellar activity}
%\jessi{Its seems that more details should be added here}
%Stellar activity can induce RV variations by a modification of the spectral line asymmetry, while any orbiting companions would induce a pure Doppler shift on \emph{all} spectral lines without modifying their shape.
%Therefore, assuming that there is no instrumental systematics, stellar activity generally induces a variation in line asymmetry that can be observed in the  FWHM of the CCF. 
%The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}. 
%An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
%Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines. To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}. A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity. 
%\comment{It is the slope or span, not both. And you generally do not calculate the inverse, just the
%span. This may be correlated or inversely correlated with the RV.}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Figueira indicators of stellar activity}
%\citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF \jessi{this needs to be better explained}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Issues with detecting stellar activity}
%Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
%In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry. All those parameters are correlated when stellar activity is dominant, and performing a step-by-step approach makes it difficult to correctly derive the errors on the different parameters retrieved. 
%\comment{I simply do not understand this statement, possibly because it does not follow a standard English construction. You have a CCF and you measure a width and bisector span. This is a measurement error determined by the S/N, the resolution, and the stability of the spectrograph. You can determine an error in a quantity (RV and BIS). You can also have an uncertainty in the contribution of activity to the RV signal, but that is not a formal error. True errors come from photon statistics, systematic errors, instrumental errors, etc. You can attempt to remove the signal due to activity and that has an associated error, but that error is due to your lack of knowledge of the surface structure causing this RV and the exact value of the contribution to the RV. This is different from a measurement error. Maybe that is what you mean here, but it is not clear from what is written.}
%In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors. We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Outline of paper}
\todo{This paragraph will need to be updated once the rest is finished.} The paper is organized as follow. In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN distribution is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF. In Sec.~\ref{intro} we present a simple model to correct for stellar activity. In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators. In Sec.~\ref{sec:5} we derive error bars for the different CCF parameters, and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.
